### 2024-01-26 Paper/paper.tex

    Based on the AHAID-EIN matches I found in the first stages of forming the executive leadership teams of hospitals, I merge the aggregated leadership information to both the American Hospital Association (AHA) survey and Hospital Compare data. From AHA, I gather the number of beds in the hospital and the Medicare number, which I use to merge in the Hospital Compare data. Hospital Compare contains multiple datasets which I use to identify hospitals that were penalized in the Hospital Readmissions Reduction Program (HRRP), along with yearly readmission and mortality rates for the relevant HRRP conditions: heart failure, heart attack, and pneumonia, my outcomes of interest.

    The Hospital Compare excess readmissions files contain hospital level information on the excess readmission measure used by CMS to determine whether a hospital should be penalized. This variable is also condition specific, where a hospital is penalized if any of the three excess readmission ratios are greater than one.

@@

>>>>

    Based on the AHA ID-EIN matches I found in the first stages of forming the executive leadership teams of hospitals, I merge the aggregated leadership information to both the American Hospital Association (AHA) survey and Hospital Compare data. From AHA, I gather the number of beds in the hospital and the Medicare number, which I use to merge in the Hospital Compare data. Hospital Compare contains multiple datasets which I use to identify hospitals that were penalized in the Hospital Readmissions Reduction Program (HRRP), along with yearly readmission and mortality rates for the relevant HRRP conditions: heart failure, heart attack, and pneumonia, my outcomes of interest.

    The Hospital Compare excess readmissions files contain hospital level information on the excess readmission measure used by CMS to determine whether a hospital should be penalized. This variable is also condition specific, where a hospital is penalized if any of the three excess readmission ratios are greater than one. Further, Hospital Compare also publishes hospital level readmission and mortality rates for heart failure, heart attack, and pneumonia. For my main outcomes of interest, I take an average across conditions and weight it using the total number of patients in that condition. For further analysis, I create samples of hospitals who were penalized for specific conditions and investigate the change in readmission and mortality rates for the condition they were penalized for.

@@

    Hospital that are not traditional for-profits maximize an
